Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-01 prob.tex
prob.tex \section{Proofs} Change the section name back to proofs...

\section{Theorems}

@@

\begin{definition}\cite{CourantJohn1965,Voevodskyothers2013}~For
any function~$f$, a function~$\varDelta_{f}:\left(0,\infty\right]\rightarrow\left(0,\infty\right]$
is a modulus of continuity of $f$ if for every $\epsilon>0$, $\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\varDelta_{f}\left(\epsilon\right)$
implies $\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|<\epsilon$.\qed\end{definition}

Notice that a function $f$ may have more than one modulus of continuity.
For example, $\varDelta_{f}\left(\epsilon\right)=\frac{\epsilon}{2}$
and $\epsilon$ are both modulus of continuity of $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
on $S^{2}$. Conversely, a function may be a modulus of continuity
of two different functions. For example, $\varDelta\left(\epsilon\right)=\frac{\epsilon}{2}$
is a modulus of continuity of both $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
and $f\left(\ket{\psi}\right)=\frac{1}{3}$ on $S^{2}$.

@@

The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.
The only significant difference is that we assume the approximation
frame function is continuous. The approximation frame function might
not be continuous as in all of our previous example, while the frame
function in original Gleason's theorem is always continuous. Thus,
we need to assume the continuity to follow the proof in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogCorollary22RichmanBridges1999}Let $f$
be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$m=\inf f$ or $m=\sup f$, and $W=\frac{W_{l}+W_{r}}{2}$. Let $Q$
be the quadratic form given by
\[
Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
\]
For each $\delta>0$, there is $\eta>0$ such that if
\begin{itemize}
\item $\left|f\left(\ket{0}\right)-m\right|<\eta$, and 
\item $g$ is the symmetrization of $f$ with respect to $\ket{0}$.
\end{itemize}
then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$.\qed\end{thm}

Since $\delta$ can be arbitrary small in theorem~\ref{thm:analogCorollary22RichmanBridges1999},
we can get the following corollary.

\begin{cor}Let $f$ be a bounded continuous approximation frame function
of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{0}\right)$
or $m=\max f=f\left(\ket{0}\right)$, and $W=\frac{W_{l}+W_{r}}{2}$.
Let $Q$ be the quadratic form given by
\[
Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)
\]
If $g$ is the symmetrization of $f$ with respect to $\ket{0}$,
then $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}

Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}Let $f$ be a bounded frame function on the unit sphere
in $\mathbb{R}^{3}$, and $\delta>0$. Then there is a quadratic form
$Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
for all $\ket{\psi}$ on the sphere.\qed\end{thm}

Currently, we can only prove the following.

@@

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}} nonnegative approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g\left(\ket{\psi}\right)\le W_{r}-\eta$ for
all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.

@@

For any point $\ket{\psi}$ in the closed northern hemisphere, consider
its longitude~$\varphi$, and a function~$F\left(a\right)=W-g\left(\ket{\psi'}\right)$,
where $\ket{\psi'}$ is a point in the closed northern hemisphere
with longitude~$\varphi$, and $a=\ell\left(\ket{\psi'}\right)$.
More specifically, let $\ket{\psi_{i}'}$ be a point in the closed
northern hemisphere with longitude~$\varphi$ such that $a_{i}=\ell\left(\ket{\psi_{i}'}\right)$.
Hence, $\ket{\psi_{i}'}$ and $\ket{\psi_{i}}$ are in the same latitude
so that 
\[
\left|F\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|=\left|g\left(\ket{\psi_{i}}\right)-g\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
\]
for all $i$. Whence, 
\begin{eqnarray*}
 &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
 & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right)\right|\\
 & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
 & \le & 3\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
\end{eqnarray*}
Therefore, by Lemma~19 in \cite{RichmanBridges1999}, 
\[
\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|W-g\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
\]
\end{proof}

>>>>

@@

@@

@@

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f$ be a nonnegative continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g\left(\ket{\psi}\right)\le W_{r}-\eta$ for
all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g$ on latitudes is at most $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)$.

@@

For any point $\ket{\psi}$ in the closed northern hemisphere, consider
its longitude~$\varphi$, and a function~$F\left(a\right)=W-g\left(\ket{\psi'}\right)$,
where $\ket{\psi'}$ is a point in the closed northern hemisphere
with longitude~$\varphi$, and $a=\ell\left(\ket{\psi'}\right)$.
More specifically, let $\ket{\psi_{i}'}$ be a point in the closed
northern hemisphere with longitude~$\varphi$ such that $a_{i}=\ell\left(\ket{\psi_{i}'}\right)$.
Hence, $\ket{\psi_{i}'}$ and $\ket{\psi_{i}}$ are in the same latitude
so that 
\[
\left|F\left(a_{i}\right)-\left(W-g\left(\ket{\psi_{i}}\right)\right)\right|=\left|g\left(\ket{\psi_{i}}\right)-g\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)\textrm{ .}
\]
for all $i$. Whence, 
\begin{eqnarray*}
 &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
 & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g\left(\ket{\psi_{0}}\right)+g\left(\ket{\psi_{1}}\right)+g\left(\ket{\psi_{2}}\right)\right)\right|\\
 & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
 & \le & 3\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
\end{eqnarray*}
Therefore, by Lemma~19 in \cite{RichmanBridges1999}, 
\[
\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|W-g\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
\]
\end{proof}
The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.

\begin{cor}\label{thm:analogCorollary22RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$,
$\eta=f\left(\ket{0}\right)-m$, 
\item $g$ be the symmetrization of $f$ with respect to $\ket{0}$,
\item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
\begin{proof}
Clearly, $f'=f-m$ is a nonnegative frame function of weight~$\left(W_{l}',W_{r}'\right)=\left(W_{l}-3m,W_{r}-3m\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
and $g'=g-2m$ be the symmetrization of $f'$ with respect to $\ket{0}$
. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
and we have $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g'\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
\end{proof}
Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}Let $f$ be a bounded continuous approximation frame function
of weight~$\left(W_{l},W_{r}\right)$ on $S^{2}$. Then there is
a quadratic form $Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le?$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Let $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$
and $m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$.
Let $\ket{2}$ and $\ket{2'}$ be the images of $\ket{\psi_{M}}$
and $\ket{\psi_{m}}$ under $90\textdegree$ rotation of the great
circle joining them. Then 
\[
\left|\left(f\left(\ket{\psi_{M}}\right)+f\left(\ket{\psi_{M}'}\right)\right)-\left(f\left(\ket{\psi_{m}}\right)+f\left(\ket{\psi_{m}'}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\psi_{m}'}\right)-f\left(\ket{\psi_{M}'}\right)\ge f\left(\ket{\psi_{M}}\right)-f\left(\ket{\psi_{m}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{\psi_{M}'}\right)\le m+W_{r}-W_{l}$ and $f\left(\ket{\psi_{m}'}\right)\ge M-\left(W_{r}-W_{l}\right)$.
\end{proof}
